% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TeX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TYPESETTING OPTIONS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\TypesetInNonStopMode}{1}
\newcommand{\TypesetInDraftMode}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVAuthor}{Abhinav Mishra}
\newcommand{\CVTitle}{}
\newcommand{\CVNote}{CV compiled on {\today}}
\newcommand{\CVWebpage}{http://www.mishrabhinav.com}
\newcommand{\GitHub}{http://www.github.com/mishrabhinav}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
bookmarks=true,
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
\href{https://www.google.co.uk/maps/place/Imperial+College+Union,+Prince+Consort+Rd,+Kensington,+London+SW7+2BB}
{EB07, Beit Hall, Prince Consort Road, London SW7 2BB, UK}
\par
\href{mailto:abhinav.mishra15@imperial.ac.uk}
{abhinav.mishra15@imperial.ac.uk}
\,\SubBulletSymbol\,
+44\,7599488182
\,\SubBulletSymbol\,
\href{www.mishrabhinav.com}
{www.mishrabhinav.com}
\par
GitHub: \href{\GitHub}{mishrabhinav}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

\href{http://www.imperial.ac.uk}
{\textbf{Imperial College London}},
United Kingdom

\GapNoBreak

\BulletItem
Bachelor of Engineering (Hons) in
Computing
\hfill
\DatestampYMD{2015}{10}{03} --
Present
\begin{detail}
\end{detail}

\BigGap
\href{http://www.thekhaitanschool.org}
{\textbf{Khaitan Public School}},
India

\GapNoBreak
\BulletItem
All India Senior Secondary Certificate Examination
\href{#}
{}
\hfill
\DatestampYMD{2013}{04}{01} --
\DatestampYMD{2015}{05}{31}
\begin{detail}
\SubBulletItem
Graduated Top of the Class.
\SubBulletItem
Subject Topper in English Core, Physics and Computer Science
\SubBulletItem
Overall Percentage: 97\%
\end{detail}

\GapNoBreak
\BulletItem
All India Senior School Examination
\href{#}
{}
\hfill
\DatestampYMD{2011}{04}{01} --
\DatestampYMD{2013}{05}{31}
\begin{detail}
\SubBulletItem
Graduated with Certificate of Merit.
\SubBulletItem
Cumulative GPA: 10 / 10
\end{detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE/PROJECTS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Work Experience / Projects}
{Work Experience/Projects}
{PDF:WorkExperience}

\BulletItem
\textbf{PiSquare - Baremetal C Game}
\hfill
\DatestampYMD{2016}{06}{18}
\begin{detail}
\GapNoBreak
\SubBulletItem
Worked in a group of 4 to develop a baremetal game for Raspberry Pi.
\SubBulletItem
Project based on C, ARM Assembly, Makefile etc.
\end{detail}

\GapNoBreak

\BulletItem
\href{https://github.com/SomeRandomTeam/}
{\textbf{Overwatch - Tracking made easy}}
\hfill
\DatestampYMD{2016}{02}{27}
\begin{detail}
\GapNoBreak
\SubBulletItem
Developed an Android application basically to track everyone subscribed to a
particular event, map them and get a list of participants using proximity kit.
\SubBulletItem
Responsible for the Android application.
\SubBulletItem
Project based on Android Studio, Java, Pusher, P2PKit etc.
\end{detail}

\GapNoBreak

\BulletItem
\href{https://github.com/SomeRandomTeam/}
{\textbf{Desky - Virtual reality, multi-desktop companion}}
\hfill
\DatestampYMD{2016}{02}{20}
\begin{detail}
\GapNoBreak
\SubBulletItem
Developed a Google cardboard application which streams all your desktop feed
to your phone, where you can view them simultaneously.
\SubBulletItem
Responsible for the Unity application and the front end.
\SubBulletItem
Project based on NodeJS, Unity, Google Cardboard etc.
\end{detail}

\GapNoBreak

\BulletItem
\href{https://github.com/SomeRandomTeam/hackatbrookes2016}
{\textbf{Age of Imperial - Online Territory Game}}
\hfill
\DatestampYMD{2016}{02}{13}
\begin{detail}
\GapNoBreak
\SubBulletItem
Developed an online multiplayer strategy based game at a hackathon.
\SubBulletItem
Responsible for the front end of the game.
\SubBulletItem
Project based on HTML5, Bootstrap, NodeJS, AngularJS, pixiJS etc.
\end{detail}

\GapNoBreak

\BulletItem
\href{https://github.com/mishrabhinav/javachess-pawnrace}
{\textbf{Pawn Race - Classic Chessboard Game}}
\hfill
\DatestampYMD{2016}{01}{14}
\begin{detail}
\GapNoBreak
\SubBulletItem
Designed and developed Pawn Racing, a classical chessboard game.
\SubBulletItem
Devised an algorithm to evaluate the board state and look for the best possible
move using techniques such as Minimax and Alpha-Beta pruning.
\SubBulletItem
Project based on Java.
\end{detail}

\GapNoBreak

\BulletItem
\href{https://github.com/SomeRandomTeam/hackkings2015}
{\textbf{Mymos – Encrypted and Dynamic Web Messenger}}
\hfill
\DatestampYMD{2015}{12}{13}
\begin{detail}
\GapNoBreak
\SubBulletItem
Developed a dynamic and encrypted web messenger at a hackathon.
\SubBulletItem
Responsible for the front end and its connection with the back end.
\SubBulletItem
Project based on HTML, Bootstrap, NodeJS, AngularJS, MongoDB etc.
\end{detail}

%%%%%%%%%%%%%%%%%%%%%
%% ACADEMIC AWARDS %%
%%%%%%%%%%%%%%%%%%%%%

\section
{Academic Achievements}
{Academic Achievements}
{PDF:AcademicAchievements}

\BulletItem
\textbf{Outstanding Group Project in Topics in Computing}
\hfill
\DatestampYM{2016}{03}
\newline
Department of Computing, Imperial College London
\begin{detail}
\SubItem
Awarded a certificate for one of the most outstanding group projects in the
course CO163.
\end{detail}

\GapNoBreak

\BulletItem
\textbf{Letter of Appreciation}
\hfill
\DatestampYMD{2015}{07}{11}
\newline
Minister of Human Resource Development,
Govt. of India
\begin{detail}
\SubItem
For exceptional performance in AISSCE 2015.
\end{detail}

\GapNoBreak

\BulletItem
\textbf{Certificate of Merit}
\hfill
\DatestampYMD{2015}{07}{11}
\newline
Central Board of Secondary Education,
India
\begin{detail}
\SubItem
For being is the top 0.1\% of successful candidates in Physics (AISSCE 2015).
\end{detail}

\GapNoBreak

\BulletItem
\textbf{Kishore Vaigyanik Protsahan Yojana Fellow}
\hfill
\DatestampYM{2014}{08}
\newline
IISc. and Department of Science and Technology, Govt. of India
\begin{detail}
\SubItem
All India Rank of 1419 in a National level scholarship exam.
\end{detail}


%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORKSHOPS/HACKATHON %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Workshops}
{Workshops}
{PDF:WorkshopsHackathons}

\BulletItem
\textbf{Data Analysis using R and Python},
\hfill
\DatestampYM{2016}{02}
\newline
Imperial College Data Science Society
\newline
A 5 session workshop teaching the basics of R and Python programming languages
and how to use them efficiently for Data Analysis.
\GapNoBreak

\BulletItem
\textbf{Capture the Flag},
\hfill
\DatestampYMD{2016}{02}{06}
\newline
BAE Systems plc.
\newline
Workshop held on system security where we had to solve certain problems as a
team of 6.

\GapNoBreak

\BulletItem
\textbf{Dark Markets: De-anonymising Tor Hidden services},
\hfill
\DatestampYMD{2015}{10}{25}
\newline
Netcraft Ltd.
\newline
Workshop held on Tor hidden services and how to find the source of these
services. We had to reveal the source of certain websites given by organisers.

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}

Java,
C,
C++,
Haskell,
\newline
AngularJS,
pixiJS,
NodeJS,
HTML,
CSS,
Bootstrap,
SQL,
MongoDB,
\newline
IntelliJ IDEA,
Eclipse,
Vim,
Atom,
\newline
{\LaTeX},
Adobe Photoshop, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Other Work\newline
Experience}
{Other Work Experience}
{PDF:OtherWorkExperience}

\href{http://www.thekhaitanschool.org}
{\textbf{Khaitan Public School}},
Noida, India

\GapNoBreak
\BulletItem
President,
Deus Ex Machina(I.T. Club)
\hfill
\DatestampYMD{2014}{04}{01} --
\DatestampYMD{2015}{05}{31}

\GapNoBreak

\BulletItem
Vice President,
Deus Ex Machina(I.T. Club)
\hfill
\DatestampYMD{2012}{10}{30} --
\DatestampYMD{2014}{03}{31}

\GapNoBreak

\BulletItem
Prefect,
Student Council
\hfill
\DatestampYM{2011}{07} --
\DatestampYMD{2013}{05}

\GapNoBreak

\BulletItem
Organiser,
Unplugged
\hfill
\DatestampYM{2011}{12} --
\DatestampYM{2015}{04}
\GapNoBreak
\SubBulletItem
Planned the annual Inter-School I.T. event for 4 consecutive years.


%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\section
{Languages}
{Languages}
{PDF:Languages}

\BulletItem
English: Full professional proficiency.

\GapNoBreak
\BulletItem
Hindi: Native proficiency.

\GapNoBreak
\BulletItem
French: Elementary proficiency.

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\section
{Interests}
{Interests}
{PDF:Interests}

Technology, Programming,
\newline
Front end development,
\newline
Swimming, Football, Table Tennis

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

\section
{References}
{References}
{PDF:References}

\BulletItem
\textbf{Mr. Nicolai Stawinoga}
\newline
Personal Tutor, First Year Coordinator
\newline
Imperial College London, U.K.
\begin{detail}
\SubItem
\href{mailto:n.stawinoga13@imperial.ac.uk}
{n.stawinoga13@imperial.ac.uk}
\,
\end{detail}

\GapNoBreak

\BulletItem
\textbf{Mrs. Poonam Mehta}
\newline
Head of Department, Computer Science
\newline
Khaitan Public School, India
\begin{detail}
\SubItem
\href{mailto:poonam.mehta15@gmail.com}
{poonam.mehta15@gmail.com}
\,
\end{detail}

\end{body}

\label{LastPage}~
\end{document}
